A tool for designing digital filters for the Hankel and Fourier transforms in potential, diffusive, and wavefield modeling

### 2018-01-18 ManuscriptGeophysics2018.tex
Add links for remaining 2 references
Add Ward and Hohmann reference

Another error test is shown in Figure~\ref{fig:skindepth1}. It shows in (a) the
amplitude of the analytical fullspace solution for a wide range of
resistivities and frequencies: $\rho=$ 1e-10$\,\Omega\,$m to 1e10\,$\Omega\,$m,
and $f =$ 1e-10\,Hz to 1e14\,Hz. In this case, the horizontal offset is set to
the skin depth, and the vertical source-receiver separation to a tenth of it,
where the skin depth is given by
%
\begin{equation}
  z_\mr{skin} = \left[\omega \sqrt{\frac{\mu\varepsilon}{2}}
  \sqrt{\left\{1 + \left(\frac{1}{\omega\varepsilon\rho}\right\}^2 \right) -1}
  \right]^{-1} \, . \\
  \label{eq:skin}
\end{equation}
%
The contour lines in the figure show the magnitude of the offset: the line with
0 is where the offset is 1\,m, the line with 3 where the offset is 1\,km, etc.
The contour lines of the offset have a knee, after which they become almost
independent of frequency. This is where the quasi static approximation breaks
down, and wave phenomena become dominant. Subplot (b) shows the relative error
of the DLF using the filter \emph{Wer201} compared to the analytical solution.
It shows nicely that the filter can be used for all cases that are in the quasi
static region, but not outside.
%
\plot*{skindepth1}{width=.8\textwidth}{(a) Amplitude of the analytical
  fullspace solution for a wide range of resistivities and frequencies. The
  contour lines show the power of the offset used for the calculation, where
  the offset is set to the skin depth. (b) Relative error of the DLF compared
  with the analytical solution. The filter \emph{Wer201} works well in the
  diffusive limit, but fails when wave phenomena become dominant.}
%

@@

\bibitem[Anderson, 1973]{USGS.73.Anderson}
Anderson, W.~L.,  1973, Fortran {IV} programs for the determination of the
  transient tangential electric field and vertical magnetic field about a
  vertical magnetic dipole for an m-layer stratified earth by numerical
  integration and digital linear filtering: USGS, {\bf PB221240}.

@@

\bibitem[Anderson, 1979]{GEO.79.Anderson}
--------, 1979, Numerical integration of related {H}ankel transforms of orders
  0 and 1 by adaptive digital filtering: Geophysics, {\bf 44}, 1287--1305.
\newblock (\href{http://doi.org/10.1190/1.1441007}{doi: 10.1190/1.1441007}).

\bibitem[Anderson, 1982]{TMS.82.Anderson}
--------, 1982, Fast {H}ankel transforms using related and lagged convolutions:
  ACM Trans. Math. Softw., {\bf 8}, 344--368.
\newblock (\href{http://doi.acm.org/10.1145/356012.356014}{doi:
  10.1145/356012.356014}).

\bibitem[Anderson, 1984]{GEO.84.Anderson}
--------, 1984, {On: “Numerical integration of related Hankel transforms by
  quadrature and continued fraction expansion” by \cite{GEO.83.Chave}}:
  Geophysics, {\bf 49}, 1811--1812.
\newblock (\href{http://doi.org/10.1190/1.1441595}{doi: 10.1190/1.1441595}).

\bibitem[Anderson, 1989]{GEO.89.Anderson}
--------, 1989, A hybrid fast {H}ankel transform algorithm for electromagnetic
  modeling: Geophysics, {\bf 54}, 263--266.
\newblock (\href{http://doi.org/10.1190/1.1442650}{doi: 10.1190/1.1442650}).

\bibitem[Bernabini and Cardarelli, 1978]{GP.78.Bernabini}
Bernabini, M., and E. Cardarelli,  1978, The use of filtered {B}essel functions
  in direct interpretation of geoelectrical soundings: Geophysical Prospecting,
  {\bf 26}, 841--852.
\newblock (\href{http://doi.org/10.1111/j.1365-2478.1978.tb01636.x}{doi:
  10.1111/j.1365-2478.1978.tb01636.x}).

\bibitem[Bichara and Lakshmanan, 1976]{GP.76.Bichara}
Bichara, M., and J. Lakshmanan,  1976, Fast automatic processing of resistivity
  soundings*: Geophysical Prospecting, {\bf 24}, 354--370.
\newblock (\href{http://doi.org/10.1111/j.1365-2478.1976.tb00932.x}{doi:
  10.1111/j.1365-2478.1976.tb00932.x}).

\bibitem[Chave, 1983]{GEO.83.Chave}
Chave, A.~D.,  1983, Numerical integration of related {H}ankel transforms by
  quadrature and continued fraction expansion: Geophysics, {\bf 48},
  1671--1686.
\newblock (\href{http://doi.org/10.1190/1.1441448}{doi: 10.1190/1.1441448}).

\bibitem[Christensen, 1990]{GP.90.Christensen}
Christensen, N.~B.,  1990, Optimized fast {H}ankel transform filters:
  Geophysical Prospecting, {\bf 38}, 545--568.
\newblock (\href{http://doi.org/10.1111/j.1365-2478.1990.tb01861.x}{doi:
  10.1111/j.1365-2478.1990.tb01861.x}).

@@

\bibitem[Das and Ghosh, 1974]{GP.74.Das}
Das, U.~C., and D.~P. Ghosh,  1974, The determination of filter coefficients
  for the computation of standard curves for dipole resistivity sounding over
  layered earth by linear digital filtering: Geophysical Prospecting, {\bf 22},
  765--780.
\newblock (\href{http://doi.org/10.1111/j.1365-2478.1974.tb00117.x}{doi:
  10.1111/j.1365-2478.1974.tb00117.x}).

\bibitem[Das et~al., 1974]{GP.74.Dasb}
Das, U.~C., D.~P. Ghosh, and D.~T. Biewinga,  1974, Transformation of dipole
  resistivity sounding measurements over layered earth by linear digital
  filtering: Geophysical Prospecting, {\bf 22}, 476--489.
\newblock (\href{http://doi.org/10.1111/j.1365-2478.1974.tb00100.x}{doi:
  10.1111/j.1365-2478.1974.tb00100.x}).

\bibitem[Das and Verma, 1980]{GP.80.Das}
Das, U.~C., and S.~K. Verma,  1980, Digital linear filter for computing type
  curves for the two-electrode system of resistivity sounding: Geophysical
  Prospecting, {\bf 28}, 610--619.
\newblock (\href{http://doi.org/10.1111/j.1365-2478.1980.tb01246.x}{doi:
  10.1111/j.1365-2478.1980.tb01246.x}).

\bibitem[Das and Verma, 1981a]{GJI.81.Das}
--------, 1981a, Numerical considerations on computing the {EM} response of
  three-dimensional inhomogeneities in a layered earth: Geophysical Journal
  International, {\bf 66}, 733--740.
\newblock (\href{http://doi.org/10.1111/j.1365-246X.1981.tb04897.x}{doi:
  10.1111/j.1365-246X.1981.tb04897.x}).

\bibitem[Das and Verma, 1981b]{GXP.81.Das}
--------, 1981b, The versatility of digital linear filters used in computing
  resistivity and em sounding curves: Geoexploration, {\bf 18}, 297--310.
\newblock (\href{http://doi.org/10.1016/0016-7142(81)90059-4}{doi:
  10.1016/0016-7142(81)90059-4}).

\bibitem[Das and Verma, 1982]{GJI.82.Das}
--------, 1982, Electromagnetic response of an arbitrarily shaped
  three-dimensional conductor in a layered earth — numerical results:
  Geophysical Journal International, {\bf 69}, 55--66.
\newblock (\href{http://doi.org/10.1111/j.1365-246X.1982.tb04935.x}{doi:
  10.1111/j.1365-246X.1982.tb04935.x}).

\bibitem[Davis et~al., 1980]{EXG.80.Davis}
Davis, P.~A., S.~A. Greenhalgh, and N.~P. Merrick,  1980, Resistivity sounding
  computations with any array using a single digital filter: Exploration
  Geophysics, {\bf 11}, 54--62.
\newblock (\href{http://library.seg.org/doi/abs/10.1071/EG980054}{doi:
  10.1071/EG980054}).

@@

\bibitem[Ghosh, 1971a]{GP.71.Ghosh}
--------, 1971a, The application of linear filter theory to the direct
  interpretation of geoelectrical resistivity sounding measurements:
  Geophysical Prospecting, {\bf 19}, 192--217.
\newblock (\href{http://doi.org/10.1111/j.1365-2478.1971.tb00593.x}{doi:
  10.1111/j.1365-2478.1971.tb00593.x}).

\bibitem[Ghosh, 1971b]{GP.71.Ghoshb}
--------, 1971b, Inverse filter coefficients for the computation of apparent
  resistivity standard curves for a horizontally stratified earth: Geophysical
  Prospecting, {\bf 19}, 769--775.
\newblock (\href{http://doi.org/10.1111/j.1365-2478.1971.tb00915.x}{doi:
  10.1111/j.1365-2478.1971.tb00915.x}).

\bibitem[Guptasarma, 1982]{GP.82.Guptasarma}
Guptasarma, D.,  1982, Optimization of short digital linear filters for
  increased accuracy: Geophysical Prospecting, {\bf 30}, 501--514.
\newblock (\href{http://doi.org/10.1111/j.1365-2478.1982.tb01320.x}{doi:
  10.1111/j.1365-2478.1982.tb01320.x}).

\bibitem[Guptasarma and Singh, 1997]{GP.97.Guptasarma}
Guptasarma, D., and B. Singh,  1997, New digital linear filters for {H}ankel
  {J}0 and {J}1 transforms: Geophysical Prospecting, {\bf 45}, 745--762.
\newblock (\href{http://doi.org/10.1046/j.1365-2478.1997.500292.x}{doi:
  10.1046/10.1046/j.1365-2478.1997.500292.x}).

\bibitem[Hunziker et~al., 2015]{GEO.15.Hunziker}
Hunziker, J., J. Thorbecke, and E. Slob,  2015, The electromagnetic response in
  a layered vertical transverse isotropic medium: {A} new look at an old
  problem: Geophysics, {\bf 80}, no. 1, F1--F18.
\newblock (\href{http://doi.org/10.1190/geo2013-0411.1}{doi:
  10.1190/geo2013-0411.1}).

\bibitem[Johansen, 1975]{GP.75.Johansen}
Johansen, H.~K.,  1975, An interactive computer/graphic-display-terminal system
  for interpretation of resistivity soundings: Geophysical Prospecting, {\bf
  23}, 449--458.
\newblock (\href{http://doi.org/10.1111/j.1365-2478.1975.tb01541.x}{doi:
  10.1111/j.1365-2478.1975.tb01541.x}).

\bibitem[Johansen and Sørensen, 1979]{GP.79.Johansen}
Johansen, H.~K., and K. Sørensen,  1979, Fast {H}ankel transforms: Geophysical
  Prospecting, {\bf 27}, 876--901.
\newblock (\href{http://doi.org/10.1111/j.1365-2478.1979.tb01005.x}{doi:
  10.1111/j.1365-2478.1979.tb01005.x}).

\bibitem[Key, 2009]{GEO.09.Key}
Key, K.,  2009, {1D} inversion of multicomponent, multifrequency marine {CSEM}
  data: {M}ethodology and synthetic studies for resolving thin resistive
  layers: Geophysics, {\bf 74}, no. 2, F9--F20.
\newblock (\href{http://doi.org/10.1190/1.3058434}{doi: 10.1190/1.3058434}).

\bibitem[Key, 2012]{GEO.12.Key}
--------, 2012, Is the fast {H}ankel transform faster than quadrature?:
  Geophysics, {\bf 77}, no. 3, F21--F30.
\newblock (\href{http://doi.org/10.1190/GEO2011-0237.1}{doi:
  10.1190/GEO2011-0237.1}).

\bibitem[Koefoed, 1968]{BK.68.Koefoed}
Koefoed, O.,  1968, The application of the kernel function in interpreting
  geoelectrical resistivity measurements: Gebrüder Borntraeger.
\newblock ({I}SBN: 9783443130022).

\bibitem[Koefoed, 1970]{GP.70.Koefoed}
--------, 1970, A fast method for determining the layer distribution from the
  raised kernel function in geoelectrical sounding: Geophysical Prospecting,
  {\bf 18}, 564--570.
\newblock (\href{http://doi.org/10.1111/j.1365-2478.1970.tb02129.x}{doi:
  10.1111/j.1365-2478.1970.tb02129.x}).

\bibitem[Koefoed, 1972]{GP.72.Koefoedb}
--------, 1972, A note on the linear filter method of interpreting resistivity
  sounding data: Geophysical Prospecting, {\bf 20}, 403--405.
\newblock (\href{http://doi.org/10.1111/j.1365-2478.1972.tb00643.x}{doi:
  10.1111/j.1365-2478.1972.tb00643.x}).

\bibitem[Koefoed, 1976]{GP.76.Koefoedb}
--------, 1976, Error propagation and uncertainty in the interpretation of
  resistivity sounding data: Geophysical Prospecting, {\bf 24}, 31--48.
\newblock (\href{http://doi.org/10.1111/j.1365-2478.1976.tb00383.x}{doi:
  10.1111/j.1365-2478.1976.tb00383.x}).

\bibitem[Koefoed and Dirks, 1979]{GP.79.Koefoed}
Koefoed, O., and F.~J.~H. Dirks,  1979, Determination of resistivity sounding
  filters by the {W}iener-{H}opf least-squares method: Geophysical Prospecting,
  {\bf 27}, 245--250.
\newblock (\href{http://doi.org/10.1111/j.1365-2478.1979.tb00968.x}{doi:
  10.1111/j.1365-2478.1979.tb00968.x}).

\bibitem[Koefoed et~al., 1972]{GP.72.Koefoed}
Koefoed, O., D.~P. Ghosh, and G.~J. Polman,  1972, Computation of type curves
  for electromagnetic depth sounding with a horizontal transmitting coil by
  means of a digital linear filter: Geophysical Prospecting, {\bf 20},
  406--420.
\newblock (\href{http://doi.org/10.1111/j.1365-2478.1972.tb00644.x}{doi:
  10.1111/j.1365-2478.1972.tb00644.x}).

\bibitem[Kong, 2007]{GP.07.Kong}
Kong, F.~N.,  2007, Hankel transform filters for dipole antenna radiation in a
  conductive medium: Geophysical Prospecting, {\bf 55}, 83--89.
\newblock (\href{http://doi.org/10.1111/j.1365-2478.2006.00585.x}{doi:
  10.1111/j.1365-2478.2006.00585.x}).

@@

\bibitem[Kumar and Das, 1977]{GP.77.Kumar}
Kumar, R., and U.~C. Das,  1977, Transformation of dipole to {S}chlumberger
  sounding curves by means of digital linear filters: Geophysical Prospecting,
  {\bf 25}, 780--789.
\newblock (\href{http://doi.org/10.1111/j.1365-2478.1977.tb01204.x}{doi:
  10.1111/j.1365-2478.1977.tb01204.x}).

\bibitem[Kumar and Das, 1978]{GP.78.Kumar}
--------, 1978, Transformation of {S}chlumberger apparent resistivity to dipole
  apparent resistivity over layered earth by the application of digital linear
  filters: Geophysical Prospecting, {\bf 26}, 352--358.
\newblock (\href{http://doi.org/10.1111/j.1365-2478.1978.tb01598.x}{doi:
  10.1111/j.1365-2478.1978.tb01598.x}).

\bibitem[Mohsen and Hashish, 1994]{GP.94.Mohsen}
Mohsen, A.~A., and E.~A. Hashish,  1994, The fast {H}ankel transform:
  Geophysical Prospecting, {\bf 42}, 131--139.
\newblock (\href{http://doi.org/10.1111/j.1365-2478.1994.tb00202.x}{doi:
  10.1111/j.1365-2478.1994.tb00202.x}).

@@

\bibitem[Newman et~al., 1986]{GEO.86.Newman}
Newman, G.~A., G.~W. Hohmann, and W.~L. Anderson,  1986, Transient
  electromagnetic response of a three-dimensional body in a layered earth:
  Geophysics, {\bf 51}, 1608--1627.
\newblock (\href{http://doi.org/10.1190/1.1442212}{doi: 10.1190/1.1442212}).

\bibitem[Nissen and Enmark, 1986]{GP.86.Nissen}
Nissen, J., and T. Enmark,  1986, An optimized digital filter for the {F}ourier
  transform: Geophysical Prospecting, {\bf 34}, 897--903.
\newblock (\href{http://doi.org/10.1111/j.1365-2478.1986.tb00500.x}{doi:
  10.1111/j.1365-2478.1986.tb00500.x}).

@@

\bibitem[O'Neill, 1975]{EXG.75.ONeill}
O'Neill, D.,  1975, Improved linear filter coefficients for application in
  apparent resistivity computations: Exploration Geophysics, {\bf 6}, 104--109.
\newblock (\href{http://library.seg.org/doi/abs/10.1071/EG975104}{doi:
  10.1071/EG975104}).

\bibitem[O'Neill and Merrick, 1984]{GP.84.ONeill}
O'Neill, D.~J., and N.~P. Merrick,  1984, A digital linear filter for
  resistivity sounding with a generalized electrode array: Geophysical
  Prospecting, {\bf 32}, 105--123.
\newblock (\href{http://doi.org/10.1111/j.1365-2478.1984.tb00720.x}{doi:
  10.1111/j.1365-2478.1984.tb00720.x}).

@@

\bibitem[Raiche et~al., 2007]{ASEG.07.Raiche}
Raiche, A., F. Sugeng, and G. Wilson,  2007, Practical {3D} {EM} inversion -
  the {P223F} software suite: ASEG Technical Program Expanded Abstracts,  1--4.
\newblock (\href{http://doi.org/10.1071/ASEG2007ab114}{doi:
  10.1071/ASEG2007ab114}).

\bibitem[Slichter, 1933]{PHY.33.Slichter}
Slichter, L.~B.,  1933, The interpretation of the resistivity prospecting
  method for horizontal structures: Physics, {\bf 4}, 307--322.
\newblock (\href{http://doi.org/10.1063/1.1745198}{doi : 10.1063/1.1745198}).

>>>>

Another error test is shown in Figure~\ref{fig:skindepth1}. It shows in (a) the
amplitude of the analytical fullspace solution for a wide range of
resistivities and frequencies: $\rho=$ 1e-10$\,\Omega\,$m to 1e10\,$\Omega\,$m,
and $f =$ 1e-10\,Hz to 1e14\,Hz. In this case, the horizontal offset is set to
the skin depth, and the vertical source-receiver separation to a tenth of it,
where the skin depth is given by \citep[e.g., ][ equation~1.49]{B.SEG.88.Ward}
%
\begin{equation}
  z_\mr{skin} = \left[\omega \sqrt{\frac{\mu\varepsilon}{2}}
  \sqrt{\left\{1 + \left(\frac{1}{\omega\varepsilon\rho}\right\}^2 \right) -1}
  \right]^{-1} \, . \\
  \label{eq:skin}
\end{equation}
%
The contour lines in the figure show the magnitude of the offset: the line with
0 is where the offset is 1\,m, the line with 3 where the offset is 1\,km, etc.
The contour lines of the offset have a knee, after which they become almost
independent of frequency. This is where the quasi static approximation breaks
down, and wave phenomena become dominant. Subplot (b) shows the relative error
of the DLF using the filter \emph{Wer201} compared to the analytical solution.
It shows nicely that the filter can be used for all cases that are in the quasi
static region, but not outside.
%
\plot*{skindepth1}{width=.8\textwidth}{(a) Amplitude of the analytical
  fullspace solution for a wide range of resistivities and frequencies. The
  contour lines show the power of the offset used for the calculation, where
  the offset is set to the skin depth. (b) Relative error of the DLF compared
  with the analytical solution. The filter \emph{Wer201} works well in the
  diffusive limit, but fails when wave phenomena become dominant.}
%

@@

\bibitem[Anderson, 1973]{USGS.73.Anderson}
Anderson, W.~L.,  1973, Fortran {IV} programs for the determination of the
  transient tangential electric field and vertical magnetic field about a
  vertical magnetic dipole for an m-layer stratified earth by numerical
  integration and digital linear filtering: USGS, {\bf PB221240}.
\newblock
  (\href{https://ntrl.ntis.gov/NTRL/dashboard/searchResults/titleDetail/PB221240.xhtml}{https://ntrl.ntis.gov\-/NTRL\-/dashboard\-/searchResults\-/titleDetail\-/PB221240.xhtml}).

@@

\bibitem[Anderson, 1979]{GEO.79.Anderson}
--------, 1979, Numerical integration of related {H}ankel transforms of orders
  0 and 1 by adaptive digital filtering: Geophysics, {\bf 44}, 1287--1305.
\newblock (\href{https://doi.org/10.1190/1.1441007}{doi: 10.1190/1.1441007}).

\bibitem[Anderson, 1982]{TMS.82.Anderson}
--------, 1982, Fast {H}ankel transforms using related and lagged convolutions:
  ACM Trans. Math. Softw., {\bf 8}, 344--368.
\newblock (\href{https://doi.org/10.1145/356012.356014}{doi:
  10.1145/356012.356014}).

\bibitem[Anderson, 1984]{GEO.84.Anderson}
--------, 1984, {On: “Numerical integration of related Hankel transforms by
  quadrature and continued fraction expansion” by \cite{GEO.83.Chave}}:
  Geophysics, {\bf 49}, 1811--1812.
\newblock (\href{https://doi.org/10.1190/1.1441595}{doi: 10.1190/1.1441595}).

\bibitem[Anderson, 1989]{GEO.89.Anderson}
--------, 1989, A hybrid fast {H}ankel transform algorithm for electromagnetic
  modeling: Geophysics, {\bf 54}, 263--266.
\newblock (\href{https://doi.org/10.1190/1.1442650}{doi: 10.1190/1.1442650}).

\bibitem[Bernabini and Cardarelli, 1978]{GP.78.Bernabini}
Bernabini, M., and E. Cardarelli,  1978, The use of filtered {B}essel functions
  in direct interpretation of geoelectrical soundings: Geophysical Prospecting,
  {\bf 26}, 841--852.
\newblock (\href{https://doi.org/10.1111/j.1365-2478.1978.tb01636.x}{doi:
  10.1111/j.1365-2478.1978.tb01636.x}).

\bibitem[Bichara and Lakshmanan, 1976]{GP.76.Bichara}
Bichara, M., and J. Lakshmanan,  1976, Fast automatic processing of resistivity
  soundings*: Geophysical Prospecting, {\bf 24}, 354--370.
\newblock (\href{https://doi.org/10.1111/j.1365-2478.1976.tb00932.x}{doi:
  10.1111/j.1365-2478.1976.tb00932.x}).

\bibitem[Chave, 1983]{GEO.83.Chave}
Chave, A.~D.,  1983, Numerical integration of related {H}ankel transforms by
  quadrature and continued fraction expansion: Geophysics, {\bf 48},
  1671--1686.
\newblock (\href{https://doi.org/10.1190/1.1441448}{doi: 10.1190/1.1441448}).

\bibitem[Christensen, 1990]{GP.90.Christensen}
Christensen, N.~B.,  1990, Optimized fast {H}ankel transform filters:
  Geophysical Prospecting, {\bf 38}, 545--568.
\newblock (\href{https://doi.org/10.1111/j.1365-2478.1990.tb01861.x}{doi:
  10.1111/j.1365-2478.1990.tb01861.x}).

@@

\bibitem[Das and Ghosh, 1974]{GP.74.Das}
Das, U.~C., and D.~P. Ghosh,  1974, The determination of filter coefficients
  for the computation of standard curves for dipole resistivity sounding over
  layered earth by linear digital filtering: Geophysical Prospecting, {\bf 22},
  765--780.
\newblock (\href{https://doi.org/10.1111/j.1365-2478.1974.tb00117.x}{doi:
  10.1111/j.1365-2478.1974.tb00117.x}).

\bibitem[Das et~al., 1974]{GP.74.Dasb}
Das, U.~C., D.~P. Ghosh, and D.~T. Biewinga,  1974, Transformation of dipole
  resistivity sounding measurements over layered earth by linear digital
  filtering: Geophysical Prospecting, {\bf 22}, 476--489.
\newblock (\href{https://doi.org/10.1111/j.1365-2478.1974.tb00100.x}{doi:
  10.1111/j.1365-2478.1974.tb00100.x}).

\bibitem[Das and Verma, 1980]{GP.80.Das}
Das, U.~C., and S.~K. Verma,  1980, Digital linear filter for computing type
  curves for the two-electrode system of resistivity sounding: Geophysical
  Prospecting, {\bf 28}, 610--619.
\newblock (\href{https://doi.org/10.1111/j.1365-2478.1980.tb01246.x}{doi:
  10.1111/j.1365-2478.1980.tb01246.x}).

\bibitem[Das and Verma, 1981a]{GJI.81.Das}
--------, 1981a, Numerical considerations on computing the {EM} response of
  three-dimensional inhomogeneities in a layered earth: Geophysical Journal
  International, {\bf 66}, 733--740.
\newblock (\href{https://doi.org/10.1111/j.1365-246X.1981.tb04897.x}{doi:
  10.1111/j.1365-246X.1981.tb04897.x}).

\bibitem[Das and Verma, 1981b]{GXP.81.Das}
--------, 1981b, The versatility of digital linear filters used in computing
  resistivity and em sounding curves: Geoexploration, {\bf 18}, 297--310.
\newblock (\href{https://doi.org/10.1016/0016-7142(81)90059-4}{doi:
  10.1016/0016-7142(81)90059-4}).

\bibitem[Das and Verma, 1982]{GJI.82.Das}
--------, 1982, Electromagnetic response of an arbitrarily shaped
  three-dimensional conductor in a layered earth — numerical results:
  Geophysical Journal International, {\bf 69}, 55--66.
\newblock (\href{https://doi.org/10.1111/j.1365-246X.1982.tb04935.x}{doi:
  10.1111/j.1365-246X.1982.tb04935.x}).

\bibitem[Davis et~al., 1980]{EXG.80.Davis}
Davis, P.~A., S.~A. Greenhalgh, and N.~P. Merrick,  1980, Resistivity sounding
  computations with any array using a single digital filter: Exploration
  Geophysics, {\bf 11}, 54--62.
\newblock (\href{https://doi.org/10.1071/EG980054}{doi: 10.1071/EG980054}).

@@

\bibitem[Ghosh, 1971a]{GP.71.Ghosh}
--------, 1971a, The application of linear filter theory to the direct
  interpretation of geoelectrical resistivity sounding measurements:
  Geophysical Prospecting, {\bf 19}, 192--217.
\newblock (\href{https://doi.org/10.1111/j.1365-2478.1971.tb00593.x}{doi:
  10.1111/j.1365-2478.1971.tb00593.x}).

\bibitem[Ghosh, 1971b]{GP.71.Ghoshb}
--------, 1971b, Inverse filter coefficients for the computation of apparent
  resistivity standard curves for a horizontally stratified earth: Geophysical
  Prospecting, {\bf 19}, 769--775.
\newblock (\href{https://doi.org/10.1111/j.1365-2478.1971.tb00915.x}{doi:
  10.1111/j.1365-2478.1971.tb00915.x}).

\bibitem[Guptasarma, 1982]{GP.82.Guptasarma}
Guptasarma, D.,  1982, Optimization of short digital linear filters for
  increased accuracy: Geophysical Prospecting, {\bf 30}, 501--514.
\newblock (\href{https://doi.org/10.1111/j.1365-2478.1982.tb01320.x}{doi:
  10.1111/j.1365-2478.1982.tb01320.x}).

\bibitem[Guptasarma and Singh, 1997]{GP.97.Guptasarma}
Guptasarma, D., and B. Singh,  1997, New digital linear filters for {H}ankel
  {J}0 and {J}1 transforms: Geophysical Prospecting, {\bf 45}, 745--762.
\newblock (\href{https://doi.org/10.1046/j.1365-2478.1997.500292.x}{doi:
  10.1046/10.1046/j.1365-2478.1997.500292.x}).

\bibitem[Hunziker et~al., 2015]{GEO.15.Hunziker}
Hunziker, J., J. Thorbecke, and E. Slob,  2015, The electromagnetic response in
  a layered vertical transverse isotropic medium: {A} new look at an old
  problem: Geophysics, {\bf 80}, no. 1, F1--F18.
\newblock (\href{https://doi.org/10.1190/geo2013-0411.1}{doi:
  10.1190/geo2013-0411.1}).

\bibitem[Johansen, 1975]{GP.75.Johansen}
Johansen, H.~K.,  1975, An interactive computer/graphic-display-terminal system
  for interpretation of resistivity soundings: Geophysical Prospecting, {\bf
  23}, 449--458.
\newblock (\href{https://doi.org/10.1111/j.1365-2478.1975.tb01541.x}{doi:
  10.1111/j.1365-2478.1975.tb01541.x}).

\bibitem[Johansen and Sørensen, 1979]{GP.79.Johansen}
Johansen, H.~K., and K. Sørensen,  1979, Fast {H}ankel transforms: Geophysical
  Prospecting, {\bf 27}, 876--901.
\newblock (\href{https://doi.org/10.1111/j.1365-2478.1979.tb01005.x}{doi:
  10.1111/j.1365-2478.1979.tb01005.x}).

\bibitem[Key, 2009]{GEO.09.Key}
Key, K.,  2009, {1D} inversion of multicomponent, multifrequency marine {CSEM}
  data: {M}ethodology and synthetic studies for resolving thin resistive
  layers: Geophysics, {\bf 74}, no. 2, F9--F20.
\newblock (\href{https://doi.org/10.1190/1.3058434}{doi: 10.1190/1.3058434}).

\bibitem[Key, 2012]{GEO.12.Key}
--------, 2012, Is the fast {H}ankel transform faster than quadrature?:
  Geophysics, {\bf 77}, no. 3, F21--F30.
\newblock (\href{https://doi.org/10.1190/GEO2011-0237.1}{doi:
  10.1190/GEO2011-0237.1}).

\bibitem[Koefoed, 1968]{BK.68.Koefoed}
Koefoed, O.,  1968, The application of the kernel function in interpreting
  geoelectrical resistivity measurements: Gebrüder Borntraeger.
\newblock (\href{https://isbnsearch.org/isbn/9783443130022}{{I}SBN:
  9783443130022}).

\bibitem[Koefoed, 1970]{GP.70.Koefoed}
--------, 1970, A fast method for determining the layer distribution from the
  raised kernel function in geoelectrical sounding: Geophysical Prospecting,
  {\bf 18}, 564--570.
\newblock (\href{https://doi.org/10.1111/j.1365-2478.1970.tb02129.x}{doi:
  10.1111/j.1365-2478.1970.tb02129.x}).

\bibitem[Koefoed, 1972]{GP.72.Koefoedb}
--------, 1972, A note on the linear filter method of interpreting resistivity
  sounding data: Geophysical Prospecting, {\bf 20}, 403--405.
\newblock (\href{https://doi.org/10.1111/j.1365-2478.1972.tb00643.x}{doi:
  10.1111/j.1365-2478.1972.tb00643.x}).

\bibitem[Koefoed, 1976]{GP.76.Koefoedb}
--------, 1976, Error propagation and uncertainty in the interpretation of
  resistivity sounding data: Geophysical Prospecting, {\bf 24}, 31--48.
\newblock (\href{https://doi.org/10.1111/j.1365-2478.1976.tb00383.x}{doi:
  10.1111/j.1365-2478.1976.tb00383.x}).

\bibitem[Koefoed and Dirks, 1979]{GP.79.Koefoed}
Koefoed, O., and F.~J.~H. Dirks,  1979, Determination of resistivity sounding
  filters by the {W}iener-{H}opf least-squares method: Geophysical Prospecting,
  {\bf 27}, 245--250.
\newblock (\href{https://doi.org/10.1111/j.1365-2478.1979.tb00968.x}{doi:
  10.1111/j.1365-2478.1979.tb00968.x}).

\bibitem[Koefoed et~al., 1972]{GP.72.Koefoed}
Koefoed, O., D.~P. Ghosh, and G.~J. Polman,  1972, Computation of type curves
  for electromagnetic depth sounding with a horizontal transmitting coil by
  means of a digital linear filter: Geophysical Prospecting, {\bf 20},
  406--420.
\newblock (\href{https://doi.org/10.1111/j.1365-2478.1972.tb00644.x}{doi:
  10.1111/j.1365-2478.1972.tb00644.x}).

\bibitem[Kong, 2007]{GP.07.Kong}
Kong, F.~N.,  2007, Hankel transform filters for dipole antenna radiation in a
  conductive medium: Geophysical Prospecting, {\bf 55}, 83--89.
\newblock (\href{https://doi.org/10.1111/j.1365-2478.2006.00585.x}{doi:
  10.1111/j.1365-2478.2006.00585.x}).

@@

\bibitem[Kumar and Das, 1977]{GP.77.Kumar}
Kumar, R., and U.~C. Das,  1977, Transformation of dipole to {S}chlumberger
  sounding curves by means of digital linear filters: Geophysical Prospecting,
  {\bf 25}, 780--789.
\newblock (\href{https://doi.org/10.1111/j.1365-2478.1977.tb01204.x}{doi:
  10.1111/j.1365-2478.1977.tb01204.x}).

\bibitem[Kumar and Das, 1978]{GP.78.Kumar}
--------, 1978, Transformation of {S}chlumberger apparent resistivity to dipole
  apparent resistivity over layered earth by the application of digital linear
  filters: Geophysical Prospecting, {\bf 26}, 352--358.
\newblock (\href{https://doi.org/10.1111/j.1365-2478.1978.tb01598.x}{doi:
  10.1111/j.1365-2478.1978.tb01598.x}).

\bibitem[Mohsen and Hashish, 1994]{GP.94.Mohsen}
Mohsen, A.~A., and E.~A. Hashish,  1994, The fast {H}ankel transform:
  Geophysical Prospecting, {\bf 42}, 131--139.
\newblock (\href{https://doi.org/10.1111/j.1365-2478.1994.tb00202.x}{doi:
  10.1111/j.1365-2478.1994.tb00202.x}).

@@

\bibitem[Newman et~al., 1986]{GEO.86.Newman}
Newman, G.~A., G.~W. Hohmann, and W.~L. Anderson,  1986, Transient
  electromagnetic response of a three-dimensional body in a layered earth:
  Geophysics, {\bf 51}, 1608--1627.
\newblock (\href{https://doi.org/10.1190/1.1442212}{doi: 10.1190/1.1442212}).

\bibitem[Nissen and Enmark, 1986]{GP.86.Nissen}
Nissen, J., and T. Enmark,  1986, An optimized digital filter for the {F}ourier
  transform: Geophysical Prospecting, {\bf 34}, 897--903.
\newblock (\href{https://doi.org/10.1111/j.1365-2478.1986.tb00500.x}{doi:
  10.1111/j.1365-2478.1986.tb00500.x}).

@@

\bibitem[O'Neill, 1975]{EXG.75.ONeill}
O'Neill, D.,  1975, Improved linear filter coefficients for application in
  apparent resistivity computations: Exploration Geophysics, {\bf 6}, 104--109.
\newblock (\href{https://doi.org/10.1071/EG975104}{doi: 10.1071/EG975104}).

\bibitem[O'Neill and Merrick, 1984]{GP.84.ONeill}
O'Neill, D.~J., and N.~P. Merrick,  1984, A digital linear filter for
  resistivity sounding with a generalized electrode array: Geophysical
  Prospecting, {\bf 32}, 105--123.
\newblock (\href{https://doi.org/10.1111/j.1365-2478.1984.tb00720.x}{doi:
  10.1111/j.1365-2478.1984.tb00720.x}).

@@

\bibitem[Raiche et~al., 2007]{ASEG.07.Raiche}
Raiche, A., F. Sugeng, and G. Wilson,  2007, Practical {3D} {EM} inversion -
  the {P223F} software suite: ASEG Technical Program Expanded Abstracts,  1--4.
\newblock (\href{https://doi.org/10.1071/ASEG2007ab114}{doi:
  10.1071/ASEG2007ab114}).

\bibitem[Slichter, 1933]{PHY.33.Slichter}
Slichter, L.~B.,  1933, The interpretation of the resistivity prospecting
  method for horizontal structures: Physics, {\bf 4}, 307--322.
\newblock (\href{https://doi.org/10.1063/1.1745198}{doi : 10.1063/1.1745198}).
